Vision-Based Automatic Accurate Landing of Drones

### 2024-10-26 Article/rexi_main_new.tex
Modify introduction and fixed pictures

\section{Introduction}
Unmanned aerial vehicles (UAVs), commonly known as drones, are aircraft that operate without an onboard pilot, controlled either through radio remote systems or autonomous onboard programs. Drones are valued for their simple yet effective design, ease of operation, flexibility, and cost-efficiency, making them versatile tools in both military and civilian domains. In military operations, they play crucial roles in tasks such as tactical reconnaissance, territorial surveillance, and target acquisition. 
On the civilian side, drones are utilized for activities like environmental monitoring, weather data collection, and infrastructure inspection. As drones become increasingly prevalent in both sectors, ensuring their safe operation—particularly during landing—has emerged as a critical concern .\\Autonomous drone operations have rapidly advanced, yet precision landing remains a significant challenge, especially in environments where GPS signals are unreliable or unavailable. GPS signals can be easily disrupted by various factors: (a) weather conditions and sunspots may weaken signals, although they typically do not hinder positioning; (b) electromagnetic interference from sources like radios and strong magnetic fields can cause varying degrees of disruption; (c) signal strength diminishes under shelters such as buildings, vehicles, insulation materials, trees, and metal components; and (d) high-rise buildings and dense urban areas can severely impact GPS signal quality. Traditional drone landing methods often rely on GPS, which proves inadequate in urban or indoor settings. This limitation poses significant challenges for applications requiring precise landings, such as urban package delivery, infrastructure inspection, and emergency response. As a result, there is a critical need to develop autonomous positioning and flight control systems for drones that do not rely on GPS signals.\\
This research addresses these challenges by developing a visual-based landing system that enhances accuracy and safety. Our approach enables drones to autonomously identify and land on planar surfaces, such as rooftops, relying solely on visual data from the onboard camera. By eliminating the need for additional sensors or external data inputs, this system offers a robust solution for autonomous landings in complex environments.

@@

\section{Drone Control Mechanisms} \label{sec:mechanisms}
\subsection{Drone Control Parameters}
The drone’s movement is governed by four fundamental control parameters: yaw, pitch, roll, and throttle. 
These parameters allow the drone to maneuver in 3D space with precision, facilitating both object tracking and navigation during various flight operations.
\begin{description}
\item $\bullet$ Yaw - controls the rotation around the vertical axis, allowing the drone to turn left or right to face objects.
\item $\bullet$ Pitch - adjusts the forward and backward tilt, moving the drone in those directions.
\item $\bullet$ Roll - manages side-to-side tilt, shifting the drone left or right.
\item $\bullet$ Throttle - regulates altitude by increasing or decreasing the drone’s lift.
\end{description}

@@

\begin{description}
\item $\bullet$ Joysticks - The left joystick controls throttle and yaw, while the right joystick manages pitch and roll, enabling intuitive movement and orientation.

\item $\bullet$ Buttons and Switches - Various buttons activate functions such as takeoff, landing, camera capture, and flight mode adjustments, enhancing operational versatility.

\item $\bullet$ Display Screen - Many controllers include a screen or connect to mobile devices to provide real-time telemetry, such as altitude, speed, and battery status, improving situational awareness.

\item $\bullet$ Communication Protocol - The controller communicates with the drone via RF signals, ensuring reliable connectivity and minimal latency during flight.

@@

The experiments were conducted in both indoor and outdoor environments. For outdoor tests, the drone was operated in real-world conditions, including on the ground and atop a table, to simulate different elevation scenarios. Additionally, the DJI Mavic Air 2 was tested in varying weather conditions, including strong winds and sunny days, to assess its performance under challenging conditions.\\
To supplement the real-world tests, a simulator was employed to thoroughly evaluate the drone’s behavior and command responsiveness in a controlled, non-real-world-based environment. This simulation allowed us to test the system's reaction to flight commands, such as takeoff, landing, edge detection, and obstacle avoidance, in a reproducible setting without the risks associated with physical testing.\\
By testing in both simulated and real environments, the drone's flight stability and command accuracy were evaluated under diverse conditions, ensuring robustness and reliability in practical applications.

\section{Algorithm Design} \label{sec:algorithm}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{landingMainExplenation.png}  % Reduced the size here
    \caption{Landing view screen while running the app.}
    \label{fig:landingMainExplenation.}
\end{figure}
Our proposed algorithm for autonomous drone landing consists of three key components: Target Line Selection, Flight Control, and Object Detection. Each part contributes to the overall reliability and precision of the landing process, ensuring safe navigation and obstacle avoidance.
Our algorithm utilizes the camera mounted on a gimbal angled at 45°.
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{Schematic_for_automatic_landing.png}  % Reduced the size here
    \caption{Schematic for automatic landing.}
    \label{fig:Schematic_for_automatic_landing.}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{Blind Spot Area.png}  % Reduced the size here
    % \caption{Schematic for automatic landing.}
    \label{fig:Blind Spot Area.}
\end{figure}

@@

Each recognized command triggers a specific action in the drone. The key commands and their associated actions are:
\begin{description}
\item $\bullet$ Takeoff - Initiates the drone's takeoff sequence, lifting it to a designated altitude for hover.
\item $\bullet$ Land - Initiates the landing sequence, lowering the throttle for a controlled descent until the drone reaches the ground.
\item $\bullet$ Stop - Halts any current movement, keeping the drone stationary in hover mode.
\item $\bullet$ Move up - Increases the throttle to elevate the drone vertically.
\item $\bullet$ Move down - Decreases the throttle, causing the drone to descend.
\item $\bullet$ Start recording - Begins video recording using the drone's camera.
\item $\bullet$ Stop recording - Stops the video recording and saves the footage.
\item $\bullet$ Edge detection - Activates the edge detection algorithm, allowing the system to identify and process edges for navigation or object tracking.
\item $\bullet$ Movement detection (Guard Mode) - Activates a security or surveillance mode where the drone monitors for movement in its environment and triggers alerts or actions based on detected motion.
\subitem $\bullet$ Start movement detection - Begins monitoring the environment for movement.
\subitem $\bullet$ Stop movement detection - Disables the movement detection and returns to normal operation.
\end{description}
This combination of commands allows users to control the drone in various situations, from basic navigation to more advanced functionality, such as edge detection and movement detection for security or surveillance purposes.

>>>>

\section{Introduction}
Unmanned aerial vehicles (UAVs), commonly known as drones, are aircraft that operate without an onboard pilot, controlled either through radio remote systems or autonomous onboard programs. Drones are valued for their simple yet effective design, ease of operation, flexibility, and cost-efficiency, making them versatile tools in both military and civilian domains. In military operations, drones play pivotal roles in tasks such as tactical reconnaissance, territorial surveillance, and target acquisition. In surveillance missions, accurate landing is especially critical, as drones must often be deployed to specific vantage points—such as rooftops or elevated positions—where stable operation is essential for continuous monitoring of target areas.\\
On the civilian side, drones are utilized for activities like environmental monitoring, weather data collection, and infrastructure inspection. As drones become increasingly prevalent in both sectors, ensuring their safe and precise landing—particularly in challenging environments—has emerged as a critical concern. In surveillance operations, an accurate landing ensures that drones can be positioned optimally to capture and monitor sensitive areas over extended periods, thus reducing the need for human intervention and minimizing the risks associated with miscalculation during deployment.\\
Autonomous drone operations have rapidly advanced, yet precision landing remains a significant challenge, especially in environments where GPS signals are unreliable or unavailable. GPS signals can be easily disrupted by various factors: (a) weather conditions and sunspots may weaken signals, although they typically do not hinder positioning; (b) electromagnetic interference from sources like radios and strong magnetic fields can cause varying degrees of disruption; (c) signal strength diminishes under shelters such as buildings, vehicles, insulation materials, trees, and metal components; and (d) high-rise buildings and dense urban areas can severely impact GPS signal quality. Traditional drone landing methods often rely on GPS, which proves inadequate in urban or indoor settings. This limitation poses significant challenges for applications requiring precise landings, such as military surveillance, urban package delivery, infrastructure inspection, and emergency response. As a result, there is a critical need to develop autonomous positioning and flight control systems for drones that do not rely on GPS signals.\\
This research addresses these challenges by developing a visual-based landing system that enhances accuracy and safety. Our approach enables drones to autonomously identify and land on strategic surfaces, such as rooftops, relying solely on visual data from the onboard camera. By eliminating the need for additional sensors or external data inputs, this system offers a robust solution for autonomous landings in complex environments, ensuring the drone is precisely positioned for effective surveillance and monitoring.

@@

\section{Drone Control Mechanisms} \label{sec:mechanisms}
\subsection{Drone Control Parameters}
The drone’s movement is governed by four fundamental control parameters: yaw, pitch, roll, and throttle.
These parameters allow the drone to maneuver in 3D space with precision, facilitating both object tracking and navigation during various flight operations.

\textbf{Yaw} - controls the rotation around the vertical axis, allowing the drone to turn left or right to face objects.

\textbf{Pitch} - adjusts the forward and backward tilt, moving the drone in those directions.

\textbf{Roll} - manages side-to-side tilt, shifting the drone left or right.

\textbf{Throttle} - regulates altitude by increasing or decreasing the drone’s lift.

@@

(a) Joysticks - The left joystick controls throttle and yaw, while the right joystick manages pitch and roll, enabling intuitive movement and orientation.

(b) Buttons and Switches - Various buttons activate functions such as takeoff, landing, camera capture, and flight mode adjustments, enhancing operational versatility.

(c) Display Screen - Many controllers include a screen or connect to mobile devices to provide real-time telemetry, such as altitude, speed, and battery status, improving situational awareness.

(d) Communication Protocol - The controller communicates with the drone via RF signals, ensuring reliable connectivity and minimal latency during flight.

@@

The experiments were conducted in both indoor and outdoor environments. For outdoor tests, the drone was operated in real-world conditions, including on the ground and atop a table, to simulate different elevation scenarios. Additionally, the DJI Mavic Air 2 was tested in varying weather conditions, including strong winds and sunny days, to assess its performance under challenging conditions.\\
To supplement the real-world tests, a simulator was employed to thoroughly evaluate the drone’s behavior and command responsiveness in a controlled, non-real-world-based environment. This simulation allowed us to test the system's reaction to flight commands, such as takeoff, landing, edge detection, and obstacle avoidance, in a reproducible setting without the risks associated with physical testing.\\
By testing in both simulated and real environments, the drone's flight stability and command accuracy were evaluated under diverse conditions, ensuring robustness and reliability in practical applications.
\subsection{Application View}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.55\textwidth]{landingMainExplenation.png}  % Reduced the size here
    \caption{Landing view screen while running the app.}
    \label{fig:landingMainExplenation.}
\end{figure}
\section{Algorithm Design} \label{sec:algorithm}

Our proposed algorithm for autonomous drone landing consists of three key components: Target Line Selection, Flight Control, and Object Detection. Each part contributes to the overall reliability and precision of the landing process, ensuring safe navigation and obstacle avoidance.
Our algorithm utilizes the camera mounted on a gimbal angled at 45°.
\begin{figure}[H]
    \centering
    \includegraphics[width=0.48\textwidth]{Schematic_for_automatic_landing.png}  % Reduced the size here
    \caption{Schematic for automatic landing.}
    \label{fig:Schematic_for_automatic_landing.}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{Blind Spot Area.png}
    \caption{Blind Spot Area.}
    \label{fig:Blind Spot Area.}
\end{figure}

@@

Each recognized command triggers a specific action in the drone. The key commands and their associated actions are:

(a) \textbf{Takeoff} - Initiates the drone's takeoff sequence, lifting it to a designated altitude for hover.

(b) \textbf{Land} - Initiates the landing sequence, lowering the throttle for a controlled descent until the drone reaches the ground.

(c) \textbf{Stop} - Halts any current movement, keeping the drone stationary in hover mode.

(d) \textbf{Move up} - Increases the throttle to elevate the drone vertically.

(e) \textbf{Move down} - Decreases the throttle, causing the drone to descend.

(g) \textbf{Start recording} - Begins video recording using the drone's camera.

(h) \textbf{Stop recording} - Stops the video recording and saves the footage.

(i) \textbf{Edge detection} - Activates the edge detection algorithm, allowing the system to identify and process edges for navigation or object tracking.

(j) \textbf{Movement detection (Guard Mode)} - Activates a security or surveillance mode where the drone monitors for movement in its environment and triggers alerts or actions based on detected motion.

(k) \textbf{Start movement detection} - Begins monitoring the environment for movement.

(l) \textbf{Stop movement detection} - Disables the movement detection and returns to normal operation.

This combination of commands allows users to control the drone in various situations, from basic navigation to more advanced functionality, such as edge detection and movement detection for security or surveillance purposes.
